\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-10 draft.tex
update appex:pi eqn
rough in proof eqns for \ga results

\begin{lemma}
  The direct effect of exogenous positive shifts in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive. \hyperlink{Pr_eg}{Proof}
	  \label{res:eg}
\end{lemma}

@@

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_eg}{Proof of Result~\ref{res:eg}}}: \\

@@

@@

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that this derivative is negative. The derivative is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:pi}
\end{equation}

@@

\vskip.4in
\noindent \textbf{\hypertarget{Pr_pi_indir}{Proof of Lemma~\ref{res:pi_indir}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\bta)}{\partial \tau^a} - \frac{\partial^2 r}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
	\]
Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive. $\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_pi_total}{Proof of Result~\ref{res:pi_total}}}: \\
$	\frac{\partial R(\bta,\tad)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$. $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}. $\frac{\partial e}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:lobby}. $\frac{\partial r}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:leg_a}. Thus the entire expression is non-positive. $\hfill\blacksquare$

>>>>

\begin{lemma}
  The direct effect of exogenous positive shifts in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive. \hyperlink{Pr_ga_dir}{Proof}
	  \label{res:ga_dir}
\end{lemma}

@@

\begin{lemma}
  Lobbying effort is weakly increasing in the uniform exogenous positive shifts of the political weighting function. \hyperlink{Pr_ga_indir}{Proof}
  \label{res:ga_indir}
\end{lemma}

\begin{result}
	The total probability that the antidumping duties will be renewed is increasing in $\ga$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$). \hyperlink{Pr_ga_total}{Proof}
	\label{res:ga_total}
\end{result}

@@

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.

This leaves room for very broad kinds of shifts in $\ga(\cdot)$.

\vskip.4in
\noindent \textbf{\hypertarget{Pr_ga_indir}{Proof of Lemma~\ref{res:ga_indir}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e}{\partial \ga(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \ga(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \ga(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \ga(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
	\]

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_ga_total}{Proof of Result~\ref{res:ga_total}}}: \\
$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$. $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}. $\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}. $\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}. Thus the entire expression is non-negative. $\hfill\blacksquare$

@@

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that this derivative is negative. The derivative is 
\begin{equation}
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:pi}
\end{equation}

@@

\vskip.4in
\noindent \textbf{\hypertarget{Pr_pi_indir}{Proof of Lemma~\ref{res:pi_indir}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e}{\partial \pi(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \pi(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
	\]
Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive. $\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_pi_total}{Proof of Result~\ref{res:pi_total}}}: \\
$\frac{\partial R(\bta,\tad)}{\partial \pi(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \pi(\cdot)} + \frac{\partial r}{\partial \pi(\cdot)}$. $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}. $\frac{\partial e}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_indir}. $\frac{\partial r}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_dir}. Thus the entire expression is non-negative. $\hfill\blacksquare$
